The Need to Develop a Holistic Infectious Disease Surveillance System

### 2024-10-22 manuscript/manuscript.qmd
Create manuscript figures directly within the manuscript file
Helps split the work into smaller sections and reduce recomputations
when sharing objects between plot and table creation scripts

```{julia}
#| fig-cap: "The accuracy of outbreak detection systems under different testing rates and noise structures. The shaded bands illustrate the 80% central interval, and the solid/dashed lines represent the mean estimate."
#| label: fig-accuracy
accuracy_line_plot
```

```{julia}
#| fig-cap: "The number of unavoidable cases of outbreak detection systems under different testing rates and noise structures. The shaded bands illustrate the 80% central interval, and the solid/dashed lines represent the mean estimate."
#| label: fig-unavoidable
unavoidable_line_plot
```

```{julia}
#| fig-cap: "The detection delay of outbreak detection systems under different testing rates and noise structures. The shaded bands illustrate the 80% central interval, and the solid/dashed lines represent the mean estimate."
#| label: fig-delay
delay_line_plot
```

For Poisson noise, similar detection delays are observed for all test and noise magnitudes, with variation by testing rate (mean of -3.7 to 36.1 days).
Under dynamical noise, there are clearer differences in the performance of ELISA and RDTs, with the separation of outcomes occurring later than observed for detection accuracy (8 time noise magnitude vs. 2 times, respectively) (@fig-accuracy).
With large amounts of dynamical noise (8 times the measles incidence), the mean detection delay of the 90% and 85% RDTs range from -17.5 days to 3.2 days, and from -25.2 days to -3.4 days, respectively.
Negative delays indicate that alerts are being triggered before the start of the outbreak and is correlated with the proportion of the time series that is under alert, with larger negative delays associated with more and/or longer alert periods (@fig-alert-proportion).

>>>>

```{julia}
#| fig-cap: "The accuracy of outbreak detection systems under different testing rates and noise structures. The shaded bands illustrate the 80% central interval, and the solid/dashed lines represent the mean estimate."
#| label: fig-accuracy
line_plot(
    optimal_threshold_characteristics;
    outcome = :accuracy,
    ylabel = "Outbreak Detection\nAccuracy",
    facet_fontsize = 18,
    labelsize = 20,
    show_x_facet_label = true,
    show_y_facet_label = false,
    ylims = (0.5, 1.0),
    force = true,
    save_plot = false,
    clinical_hline = clinical_hline,
)
```

```{julia}
#| fig-cap: "The number of unavoidable cases of outbreak detection systems under different testing rates and noise structures. The shaded bands illustrate the 80% central interval, and the solid/dashed lines represent the mean estimate."
#| label: fig-unavoidable
line_plot(
    optimal_threshold_characteristics;
    outcome = :unavoidable_cases,
    ylabel = "Unavoidable Cases",
    facet_fontsize = 18,
    labelsize = 20,
    show_x_facet_label = true,
    show_y_facet_label = false,
    ylims = (0, 3.5e4),
    force = true,
    save_plot = false,
    clinical_hline = clinical_hline,
)
```

```{julia}
#| fig-cap: "The detection delay of outbreak detection systems under different testing rates and noise structures. The shaded bands illustrate the 80% central interval, and the solid/dashed lines represent the mean estimate."
#| label: fig-delay
line_plot(
    optimal_threshold_characteristics;
    outcome = :detectiondelays,
    ylabel = "Detection Delays\n(Days)",
    hlines = (0.0),
    facet_fontsize = 18,
    labelsize = 20,
    show_x_facet_label = true,
    show_y_facet_label = false,
    ylims = (-100, 100),
    force = true,
    save_plot = false,
    clinical_hline = clinical_hline,
)
```

For Poisson noise, similar detection delays are observed for all test and noise magnitudes, with variation by testing rate (mean of -3.7 to 36.1 days).
Under dynamical noise, there are clearer differences in the performance of ELISA and RDTs, with the separation of outcomes occurring later than observed for detection accuracy (8 time noise magnitude vs. 2 times, respectively) (@fig-accuracy).
With large amounts of dynamical noise (8 times the measles incidence), the mean detection delay of the 90% and 85% RDTs range from -17.5 days to 3.2 days, and from -25.2 days to -3.4 days, respectively.
Negative delays indicate that alerts are being triggered before the start of the outbreak and is correlated with the proportion of the time series that is under alert, with larger negative delays associated with more and/or longer alert periods (@fig-alert-proportion, Supplemental Figure 2).
